---
title: "Gov 50 Final Project"
author: "Darley Boit"
description: "My final project"
output:
  distill::distill_article:
    self_contained: false
---



## Project thoughts

I am interested in exploring data related to identity, specifically the Hispanic/Latinx identity in the United States.This data set from the Pew Research Center analyzes how individuals with Hispanic/Latinx ancestry do or do not identify with the terms. 

This is of particular interest to me as a dual citizen with Brazil (where my grandfather is from). I myself tend to identify as white -- especially if the only two options are 'white, not hispanic/latino' or 'hispanic/latino', and if there is no overlap between the two. I would generally tend to identify more with Brazil than with any Latin identity, especially as I am racially white. I think it is relatively common among Latin/Hispanic people to identify most strongly with orgin country... thus I will also take origin country into account in this study. 

I would like to examine how individuals WITH HISPANIC/LATIN heritage identify racially. I will only look at participants with some sort of hispanic/latin ancestry. I'm thinking of having three main variables: race (hispanic or latino vs. not hispanic/latino); hispanic/latin ancestry (either yes or no); and grouping of origin country. 

Those with hispanic/latin heritage who identify as hispanic/latin will be considered "self identifying". Those with only ancestry of, but no racial self-identification, will be what I hope to explain through examining this dataset. 

https://www.pewresearch.org/hispanic/dataset/2016-survey-of-self-identified-non-hispanics-with-hispanic-ancestry/



```{r}
library(foreign)
install.packages
```


```{r}
library("haven")
library(tidyverse)
library(infer)


setwd("~/<Your File Path Here>/January 3-10, 2018 - Core Trends Survey")
jan_core_trends_survey <- read_csv("January 3-10, 2018 - Core Trends Survey - CSV.csv")

read_sav("NSL2015Omnibus_FOR_RELEASE.sav")
```









